Design Document for Relevance-Weighting: R Package glmm

### 2019-06-27 DesignDocs/DesignDocWeights.tex
updated design doc

\section{The Process}
First, the function will need to establish whether the user has supplied a proper weighting scheme. Next, the weighting scheme will need to be applied in the \texttt{el.C} function. After defining the weighting vector, the remainder of this section will illustrate how this weighting scheme will be applied.

\subsection{The Weighting Vector}
The weights must be in the form of a vector and the vector must be the same length as the response vector, $y$. All weights must be numeric and non-negative. There can be no missing weights.

@@

\begin{align}
\dfrac{\partial}{\partial \beta_l} \log \text{RWLD}(\theta) &= \lambda \ X \left[ y- c'(\eta) \right]
\end{align}

@@

\begin{align}
\dfrac{\partial^2}{\partial \beta_l^2} \log \text{RWLD}(\theta) &= \lambda \ X' \left[- c''(\eta) \right] X
\end{align}

>>>>

\section{The Process}
First, the function will need to establish whether the user has supplied a proper weighting scheme. Next, the weighting scheme will need to be applied in the \texttt{el.C}, \texttt{elval.C} and \texttt{elGH.C} functions. After defining the weighting vector, the remainder of this section will illustrate how this weighting scheme will be applied in the previously mentioned functions. Lastly, the changes made to the importance sampling distribution are outlined.

\subsection{The Weighting Vector}
If a proper weighting scheme has been supplied, the function will utilize that weighting scheme; if  the weighting scheme supplied is improper, the user will receive an error; and if no weighting scheme is supplied, a weighting vector of all ones will be created. The weights must be in the form of a vector and the vector must be the same length as the response vector, $y$. All weights must be numeric and non-negative. There can be no missing weights.

@@

\begin{align}
\dfrac{\partial}{\partial \beta_l} \log \text{RWLD}(\theta) &= \Lambda \ X \left[ y- c'(\eta) \right]
\end{align}

\noindent where $\Lambda$ is the $n$ x $n$ weight matrix made from $\lambda$, which is the $n$ x $1$ weights vector given by the user or made of all ones if no vector is given.

@@

\begin{align}
\dfrac{\partial^2}{\partial \beta_l^2} \log \text{RWLD}(\theta) &= X' \left[- c''(\eta) \right] \Lambda \ X
\end{align}

\subsection{The Importance Sampling Distribution}

The original importance sampling distribution is

\begin{align}
\tilde{f}(u) &= p_1  \grave{f}(u|0,D^*)+p_2  f(u \, | \, u^*, D^*)+p_3  f(u \, | \, u^*, (Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})
\end{align}

\noindent and the portion that is concerned with weighting is $Z' c"(X \beta^* + Zu^*) Z$. We know that $\eta = X \beta + Zu$, so this is similar to $Z' c"(\eta) Z$ which looks similar to the second derivative of the cumulant. That similarity is used to incorporate the weighting scheme into the importance sampling distribution.

The weighted version of the importance sampling distribution follows as

\begin{align}
\tilde{f}(u) &= p_1  \grave{f}(u|0,D^*)+p_2  f(u \, | \, u^*, D^*)+p_3  f(u \, | \, u^*, (Z'  c''(X \beta^*+Zu^*) \Lambda \ Z +(D^*)^{-1}   )^{-1}) \\
&= p_1 \exp( \log  \grave{f}(u|0,D^*) ))+p_2 \exp( \log(  f(u \, | \, u^*, D^*) ))+ \nonumber \\
&+ p_3 \exp( \log( f(u \, | \, u^*, (Z'  c''(X \beta^*+Zu^*) \Lambda \ Z +(D^*)^{-1}   )^{-1}) )).
\end{align}

\noindent Then, if we set

\begin{align}
\tilde{a}= \max \left\{ \log  \grave{f}(u|0,D^*) ), \log  f(u \, | \, u^*, D^*) ), \log f(u \, | \, u^*, (Z'  c''(X \beta^*+Zu^*) \Lambda \ Z +(D^*)^{-1}   )^{-1})  \right\}
\end{align}

Then,

\begin{align}
 \tilde{f}(u) 
&= p_1 \exp\left( \log  \grave{f}(u|0,D^*)  -\tilde{a}\right)+p_2 \exp \left( \log  f(u \, | \, u^*, D^* )-\tilde{a} \right)+ \nonumber\\
&+ p_3 \exp\left[ \log f \left(u \, | \, u^*, (Z'  c''(X \beta^*+Zu^*) \Lambda \ Z +(D^*)^{-1}   )^{-1} \right)  -\tilde{a} \right].
\end{align}
